---
title: "Estimate the reproduction number"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(socialmixr)
library(dplyr)
library(here)
library(ggplot2)
library(tidyverse)
library(ggthemes)
library(cowplot)
library(reshape2)
library(ipumsr)
library(grid)
library(extrafont)

# load some functions
source(here('bics-paper-code', 'code', 'utils.R'))

out.dir <- here('bics-paper-code', 'out')


```

Load all data
```{r}
## survey data
# set polymod parameters for fetching data
polymod_country = "United Kingdom"
polymod_age_limits = c(0, 18, 25, 35, 45,  65)

# polymod
polymod_mat <- getPolymodMatrix(polymod_country = polymod_country,
                                polymod_age_limits= polymod_age_limits)

polymod_mat_fb_age <- getPolymodMatrix(polymod_country = polymod_country,
                                polymod_age_limits= c(0, 15, 25, 35, 45,  65))


# polymod without school contacts
polymod_no_school_mat <- getPolymodMatrixNoSchool(polymod_country = polymod_country,
                                                  polymod_age_limits= polymod_age_limits)


# grab age distns with kids included for making contact matrix symmetric
acs18_agecat_withkids_targets <- readRDS(file=here('bics-paper-code', 'data', 'ACS', 'acs18_wave1_agecat_withkids.rds'))

# grab 2015 acs data for the FB matrix
acs15 <- read_ipums_micro(ddi=here('bics-paper-code', 'data', 'ACS', 'usa_00008.xml'))
acs15_agecat_fb <- acs15 %>%
  mutate(agecat = case_when(
    AGE %in%  0:15  ~ '[0,15)',
    AGE %in% 15:24 ~ '[15,25)',
    AGE %in% 25:34 ~ '[25,35)',
    AGE %in% 35:44 ~ '[35,45)',
    AGE %in% 45:64 ~ '[45,65)',
    AGE >= 65      ~ '[65,100]')
  ) %>%
  select(agecat, PERWT) %>%
  group_by(agecat) %>%
  summarize(acs_tot = sum(PERWT))

## wave 3 data 
wave3 <- readRDS(file=here('bics-paper-code', 'data', 'contact-matrices', 'wave3_contact_matrix_w0age.rds')) %>%
  rename(ego_age =.ego_age, alter_age=.alter_age) %>%
  filter(ego_age != "[0,18)") %>%
  filter(!is.na(alter_age))


## wave 2 data 
wave2 <- readRDS(file=here('bics-paper-code', 'data', 'contact-matrices', 'wave2_contact_matrix_w0age.rds')) %>%
  rename(ego_age =.ego_age, alter_age=.alter_age) %>%
  filter(ego_age != "[0,18)") %>%
  filter(!is.na(alter_age))


## wave 1 data
wave1 <- readRDS(file=here('bics-paper-code', 'data', 'contact-matrices', 'wave1_contact_matrix_w0age.rds')) %>%
  rename(ego_age =.ego_age, alter_age=.alter_age) %>%
  filter(ego_age != "[0,18)") 

## wave 0 data
wave0 <- readRDS(here('bics-paper-code', 'data', 'contact-matrices', "wave0_contact_matrix_w0age.rds")) %>%
  rename(ego_age =.ego_age, alter_age=.alter_age) %>%
  filter(ego_age != "[0,18)") %>%
  filter(!is.na(alter_age))

## create a list object with the data from each wave
wave_df_list <- list(wave0, wave1, wave2, wave3)
num_waves <-length(wave_df_list)

## 2015 facebook study
fb <- readRDS(file=here('bics-paper-code', 'data', 'contact-matrices', 'fb_contact_matrix_fbage.rds')) %>%
  rename(ego_age = .ego_age, alter_age = .alter_age)  %>%
  filter(ego_age != "[0,15)") 
```

Adjust for reciprocity and infer within group contacts for youngest age group

```{r}
# BICS
filled_matrix_BICS <- survey_mat_youngest_added_BICS <- list()
for (n in 1:num_waves) {
  filled_matrix_BICS[[n]] <- fill_matrix_BICS(df = wave_df_list[[n]], 
                                              age_df = acs18_agecat_withkids_targets,
                                              fill_mat = polymod_no_school_mat)
  survey_mat_youngest_added_BICS[[n]] <- filled_matrix_BICS[[n]]$survey_mat_youngest_added
}

# 2015 FB study (baseline)
filled_matrix_fb <- fill_matrix_FB(df = fb, 
                                     age_df = acs15_agecat_fb,
                                     fill_mat = polymod_mat_fb_age) # fill FB matrix assuming kids are going to school (i.e. business as usual)
survey_mat_youngest_added_fb<- filled_matrix_fb$survey_mat_youngest_added


```

Relative ratios of eigenvalues 

```{r}
#BICS compared to polymod
ratio_BICS_polymod <- list()
for (n in 1:num_waves){
  ratio_BICS_polymod[[n]] <- getRelativeR0(survey_mat = survey_mat_youngest_added_BICS[[n]],
                                           comparison_mat = polymod_mat)
}

#BICS compared to 2015 FB study
ratio_BICS_fb <- list()
for (n in 1:num_waves){
  ratio_BICS_fb[[n]] <- getRelativeR0(survey_mat = survey_mat_youngest_added_BICS[[n]],
                                           comparison_mat = survey_mat_youngest_added_fb)
}

```

Load bootstrap data and calculate \(R_0\) and confidence intervals

```{r}

sum_sym_avg_fb_bootstrapped <- readRDS(file.path(out.dir, 'sum_sym_avg_fb_bootstrapped.rds'))
sum_sym_avg_BICS_bootstrapped <- readRDS(file.path(out.dir, 'sum_sym_avg_BICS_bootstrapped.rds'))

ratio_bootstrapped_fb_baseline <- readRDS(file.path(out.dir, 'ratio_bootstrapped_fb_baseline.rds'))

R0_bootstrapped_polymod_baseline <- readRDS(file.path(out.dir, 'R0_bootstrapped_polymod_baseline.rds'))
R0_bootstrapped_fb_baseline <- readRDS(file.path(out.dir, 'R0_bootstrapped_fb_baseline.rds'))

baseline_R0 = 2.5 
baseline_R0_SE = 0.54
num_replicates <- nrow(ratio_bootstrapped_fb_baseline)
num_waves <-length(wave_df_list)

```


\(R_0\) estimate and 95% confidence intervals

```{r}
# polymod baseline: R0 est + ci
R0_est_polymod_baseline <- lapply(ratio_BICS_polymod, function(x) x*baseline_R0)
ci_R0_est_polymod_baseline <- list()
for (n in 1:num_waves) {
  ci_R0_est_polymod_baseline[[n]] <- calc_R0_ci_percentile(R0_bootstrapped_est = R0_bootstrapped_polymod_baseline[,n])
  
}

#fb baseline: R0 est + ci
R0_est_fb_baseline <- lapply(ratio_BICS_fb, function(x) x*baseline_R0)
ci_R0_est_fb_baseline <- list()
for (n in 1:num_waves) {
  ci_R0_est_fb_baseline[[n]] <- calc_R0_ci_percentile(R0_bootstrapped_est = R0_bootstrapped_fb_baseline[,n])
  
}


# % decline
(1 - unlist(ratio_BICS_fb))*100

# % decline in R0 : CI
ci_ratio_fb_baseline <- list()
for (n in 1:num_waves){
  ci_ratio_fb_baseline[[n]] <- (1-calc_R0_ci_percentile(R0_bootstrapped_est = ratio_bootstrapped_fb_baseline[,n]))*100
}

```


Plot \(R_0\) estimates

```{r}
plot_df_r0_ci <- as.data.frame(cbind(type = "Baseline", comparison = "Baseline", 
                                     r0 = baseline_R0, 
                                     ci_low = baseline_R0 - 1.96*baseline_R0_SE, 
                                     ci_high = baseline_R0 + 1.96*baseline_R0_SE)) %>%
  rbind(cbind(type = "Wave 0", comparison = "FB",
              r0 = R0_est_fb_baseline[[1]], 
              ci_low = ci_R0_est_fb_baseline[[1]][1], 
              ci_high = ci_R0_est_fb_baseline[[1]][2])) %>%
  rbind(cbind(type = "Wave 1", comparison = "FB",
              r0 = R0_est_fb_baseline[[2]], 
              ci_low = ci_R0_est_fb_baseline[[2]][1], 
              ci_high = ci_R0_est_fb_baseline[[2]][2])) %>%
  rbind(cbind(type = "Wave 2", comparison = "FB",
              r0 = R0_est_fb_baseline[[3]], 
              ci_low = ci_R0_est_fb_baseline[[3]][1], 
              ci_high = ci_R0_est_fb_baseline[[3]][2])) %>%
  rbind(cbind(type = "Wave 3", comparison = "FB",
              r0 = R0_est_fb_baseline[[4]], 
              ci_low = ci_R0_est_fb_baseline[[4]][1], 
              ci_high = ci_R0_est_fb_baseline[[4]][2])) %>%
  rbind(cbind(type = "Wave 0", comparison = "POLYMOD",
              r0 = R0_est_polymod_baseline[[1]], 
              ci_low = ci_R0_est_polymod_baseline[[1]][1], 
              ci_high = ci_R0_est_polymod_baseline[[1]][2])) %>%
  rbind(cbind(type = "Wave 1", comparison = "POLYMOD",
              r0 = R0_est_polymod_baseline[[2]], 
              ci_low = ci_R0_est_polymod_baseline[[2]][1], 
              ci_high = ci_R0_est_polymod_baseline[[2]][2])) %>%
  rbind(cbind(type = "Wave 2", comparison = "POLYMOD",
              r0 = R0_est_polymod_baseline[[3]], 
              ci_low = ci_R0_est_polymod_baseline[[3]][1], 
              ci_high = ci_R0_est_polymod_baseline[[3]][2])) %>%
  rbind(cbind(type = "Wave 3", comparison = "POLYMOD",
              r0 = R0_est_polymod_baseline[[4]], 
              ci_low = ci_R0_est_polymod_baseline[[4]][1], 
              ci_high = ci_R0_est_polymod_baseline[[4]][2])) %>%
  mutate(r0 = as.numeric(as.character(r0)), ci_low = as.numeric(as.character(ci_low)), ci_high=as.numeric(as.character(ci_high)))

R0plot <- plot_df_r0_ci %>% 
  ggplot(aes(x=type, y = r0, group = comparison, color = comparison)) +
  scale_color_manual(name = "Relative to", values = c("black", "blue", "maroon")) +
  geom_errorbar(width=.1, aes(ymin=ci_low, ymax=ci_high), position=position_dodge(width=0.5)) +
  geom_point(shape=19, size=3, fill="white", position=position_dodge(width=0.5)) +
  geom_hline(yintercept = 1, col = "black", linetype = "dotted")+
  labs(y = expression(R[0]~estimate), x = "")+
  theme_classic(base_size = 8) +
  theme(legend.position="bottom")



ggsave(R0plot, file = here("bics-paper-code", "out","R0_figure.png"), width = 6, height = 4)
ggsave(R0plot, file = here("bics-paper-code", "out","R0_figure.pdf"), width = 6, height = 4)

R0plot


```

Plot age-structured contact matrices

```{r}
xlabel <- "Age of participant"
ylabel <- "Age of contact"

mix_plot_filled_in_BICS <- list()

for (n in 1:num_waves) {
  mix_plot_filled_in_BICS[[n]] <- melt(survey_mat_youngest_added_BICS[[n]]) %>%
    rename(ego_age = Var1, alter_age = Var2, sym_avg_per_ego = value) %>%
    mutate(ego_age = case_when(ego_age == "[0,18)" ~ "[0,18)*",
                               TRUE ~ as.character(ego_age)),
           alter_age = case_when(alter_age == "[0,18)" ~ "[0,18)*",
                                 TRUE ~ as.character(alter_age))) %>%
    ggplot(.) + 
    geom_tile(aes(x=ego_age, y=alter_age, fill=sym_avg_per_ego)) +
    theme_classic(base_size = 8) +
    theme(axis.text.x=element_text(angle=90,hjust=1, vjust=.5)) +
    coord_equal() +
    xlab(xlabel) +
    ylab(ylabel) +
    viridis::scale_fill_viridis(name="Average \nnumber \nof contacts", limits=c(0, 3)) 
  
}




# BICS versus 2015 study
mix_plot_BICS_FB_compare <- list()
fb_tmp <- melt(survey_mat_youngest_added_fb) %>%
  rename(ego_age = Var1, alter_age = Var2, sym_avg_per_ego = value) %>%
  filter(!(ego_age %in% c("[0,15)", "[15,25)"))) %>%
  filter(!( alter_age %in% c("[0,15)", "[15,25)")))


for (n in 1:num_waves) {
  mix_plot_BICS_FB_compare[[n]] <- melt(survey_mat_youngest_added_BICS[[n]]) %>%
    rename(ego_age = Var1, alter_age = Var2, sym_avg_per_ego_BICS = value) %>%
    filter(!(ego_age %in% c("[0,18)", "[18,25)") & alter_age %in% c("[0,18)", "[18,25)")))  %>%
    mutate(ego_age = case_when(ego_age == "[0,18)" ~ "[0,18)**",
                               ego_age == "[18,25)" ~ "[18,25)**",
                               TRUE ~ as.character(ego_age)),
           alter_age = case_when(alter_age == "[0,18)" ~ "[0,18)**",
                                 alter_age == "[18,25)" ~ "[18,25)**",
                                 TRUE ~ as.character(alter_age))) %>%
    left_join(.,fb_tmp) %>%
    mutate(diff = sym_avg_per_ego - sym_avg_per_ego_BICS) %>%
    ggplot(.) + 
    geom_tile(aes(x=ego_age, y=alter_age, fill=diff)) +
    theme_classic(base_size = 8) +
    theme(axis.text.x=element_text(angle=90,hjust=1, vjust=.5)) +
    coord_equal() +
    xlab(xlabel) +
    ylab(ylabel) +
    viridis::scale_fill_viridis(option = "cividis", 
                                name="Difference \nin average \nnumber \nof contacts", limits = c(-0.25,5), na.value = "white")
  
}

# barplots
agegroups_fb <- row.names(survey_mat_youngest_added_fb)
ci_low_fb <- ci_high_fb <- rep(NA, length(agegroups_fb))
for (a in 1:length(agegroups_fb)){
  ci_low_fb[a] <- quantile(unlist(purrr::map(sum_sym_avg_fb_bootstrapped, agegroups_fb[a])), 0.025)
  ci_high_fb[a] <- quantile(unlist(purrr::map(sum_sym_avg_fb_bootstrapped, agegroups_fb[a])), 0.975)
}
ci_fb <- as.data.frame(cbind(ego_age = agegroups_fb, ci_low = ci_low_fb, ci_high = ci_high_fb, type = "Baseline"))

mix_plot_BICS_FB_compare_2 <- list()

fb_tmp <- melt(survey_mat_youngest_added_fb) %>%
  rename(ego_age = Var1, alter_age = Var2, sym_avg_per_ego = value) %>%
  mutate(type = "Baseline")


for (n in 1:num_waves) {
  
  # get ci
  agegroups_BICS <- row.names(survey_mat_youngest_added_BICS[[n]])
  ci_low_BICS <- ci_high_BICS <- rep(NA, length(agegroups_BICS))
  for (a in 1:length(agegroups_BICS)){
    ci_low_BICS[a] <-   sum_sym_avg_BICS_bootstrapped %>% map(list(n, agegroups_BICS[a])) %>% unlist() %>% quantile(., 0.025)
    ci_high_BICS[a] <-  sum_sym_avg_BICS_bootstrapped %>% map(list(n, agegroups_BICS[a])) %>% unlist() %>% quantile(., 0.975)
  }
  
  ci_BICS <- as.data.frame(cbind(ego_age = agegroups_BICS, ci_low = ci_low_BICS, ci_high = ci_high_BICS, type = "BICS")) 
  ci_all <- rbind(ci_BICS, ci_fb)
  
  mix_plot_BICS_FB_compare_2[[n]] <- melt(survey_mat_youngest_added_BICS[[n]]) %>%
    rename(ego_age = Var1, alter_age = Var2, sym_avg_per_ego = value) %>%
    mutate(type = "BICS") %>%
    rbind(.,fb_tmp) %>%
    filter(!is.na(alter_age)) %>%
    group_by(ego_age, type) %>%
    summarize(average = sum(sym_avg_per_ego, na.rm = TRUE)) %>%
    left_join(.,ci_all, by = c("ego_age", "type")) %>%
    mutate(ego_age = case_when(ego_age == "[0,18)" ~ "[0,18)**",
                               ego_age == "[18,25)" ~ "[18,25)**",
                               TRUE ~ as.character(ego_age))) %>%
    filter(!(ego_age %in% c("[0,15)", "[15,25)"))) %>%
    mutate(ci_high = as.numeric(as.character(ci_high)),
           ci_low = as.numeric(as.character(ci_low))) %>%
    
    
    ggplot(.) +
    geom_col(aes(x = ego_age, y = average, fill = type),position = position_identity()) +
    geom_errorbar(aes(x = ego_age, ymin=ci_low, ymax=ci_high, fill = type), width = 0.2) +
    theme_classic(base_size = 8) +
    theme(axis.text.x=element_text(angle=90,hjust=1, vjust=.5), legend.title =element_blank()) +
    xlab(xlabel) +
    ylab("Average number \nof contacts") +
    scale_fill_brewer(palette="Blues") 
}


leg1 <- get_legend(mix_plot_filled_in_BICS[[1]] + theme(legend.position="bottom"))
leg2 <- get_legend(mix_plot_BICS_FB_compare[[1]] + theme(legend.position="bottom"))
leg3 <- get_legend(mix_plot_BICS_FB_compare_2[[1]] + theme(legend.position="bottom"))

plt1 <- ggpubr::ggarrange(mix_plot_filled_in_BICS[[1]] + theme(legend.position="none"),
                          mix_plot_BICS_FB_compare[[1]]+ theme(legend.position="none"),
                          mix_plot_BICS_FB_compare_2[[1]]+ theme(legend.position="none"), 
                          mix_plot_filled_in_BICS[[2]]+ theme(legend.position="none"), 
                          mix_plot_BICS_FB_compare[[2]]+ theme(legend.position="none"),
                          mix_plot_BICS_FB_compare_2[[2]]+ theme(legend.position="none"), 
                          mix_plot_filled_in_BICS[[3]]+ theme(legend.position="none"), 
                          mix_plot_BICS_FB_compare[[3]]+ theme(legend.position="none"),
                          mix_plot_BICS_FB_compare_2[[3]]+ theme(legend.position="none"), 
                          mix_plot_filled_in_BICS[[4]]+ theme(legend.position="none"), 
                          mix_plot_BICS_FB_compare[[4]]+ theme(legend.position="none"),
                          mix_plot_BICS_FB_compare_2[[4]]+ theme(legend.position="none"),
                          ncol = 3,nrow = 4,
                          labels = c("A", "E", "I", "B", "F", "J", "C", "G", "K", "D", "H", "L"))



legends <- plot_grid(leg1, leg2, leg3, nrow = 1)
mat_plot <- ggpubr::ggarrange(plt1, legends,
                              nrow = 2, heights = c(9,1)) 
mat_plot_final <- ggpubr::annotate_figure(mat_plot,
                                          bottom = ggpubr::text_grob("* NB: Within-group mixing for the [0,18) group was estimated using POLYMOD UK data \n** NB: Youngest age-groups had different widths in the baseline survey", color = "black",
                                                                     hjust = 1, x = 1, size = 8))



ggsave(mat_plot_final, file = here("bics-paper-code","out", "matrices.png"), width = 8, height = 9)
ggsave(mat_plot_final, file = here("bics-paper-code","out", "matrices.pdf"), width = 8, height = 9)

mat_plot_final
```


Load contact matrix and bootstrap resamples, now only keeping contacts without mask usage reported, and calculate \(R_0\) and confidence intervals

```{r}
# Note: Wave 0 did not collect data on mask usage
## wave 3 data 
wave3_nomask <- readRDS(file=here('bics-paper-code', 'data', 'contact-matrices', 'wave3_contact_matrix_w0age_nomask.rds')) %>%
  rename(ego_age =.ego_age, alter_age=.alter_age) %>%
  filter(ego_age != "[0,18)") %>%
  filter(!is.na(alter_age))



## wave 2 data 
wave2_nomask <- readRDS(file=here('bics-paper-code', 'data', 'contact-matrices', 'wave2_contact_matrix_w0age_nomask.rds')) %>%
  rename(ego_age =.ego_age, alter_age=.alter_age) %>%
  filter(ego_age != "[0,18)") %>%
  filter(!is.na(alter_age))


## wave 1 data
wave1_nomask <- readRDS(file=here('bics-paper-code', 'data', 'contact-matrices', 'wave1_contact_matrix_w0age_nomask.rds')) %>%
  rename(ego_age =.ego_age, alter_age=.alter_age) %>%
  filter(ego_age != "[0,18)") 

## create a list object with the data from each wave
wave_df_list <- list(wave1_nomask, wave2_nomask, wave3_nomask)
num_waves <-length(wave_df_list)

## Adjust for reciprocity and infer within group contacts for youngest age group


# BICS - no mask
filled_matrix_BICS <- survey_mat_youngest_added_BICS <- list()
for (n in 1:num_waves) {
  filled_matrix_BICS[[n]] <- fill_matrix_BICS(df = wave_df_list[[n]], 
                                              age_df = acs18_agecat_withkids_targets,
                                              fill_mat = polymod_no_school_mat)
  survey_mat_youngest_added_BICS[[n]] <- filled_matrix_BICS[[n]]$survey_mat_youngest_added
}

## Relative ratios of eigenvalues 

#BICS compared to polymod
ratio_BICS_polymod_nomask <- list()
for (n in 1:num_waves){
  ratio_BICS_polymod_nomask[[n]] <- getRelativeR0(survey_mat = survey_mat_youngest_added_BICS[[n]],
                                           comparison_mat = polymod_mat)
}

#BICS compared to 2015 FB study
ratio_BICS_fb_nomask <- list()
for (n in 1:num_waves){
  ratio_BICS_fb_nomask[[n]] <- getRelativeR0(survey_mat = survey_mat_youngest_added_BICS[[n]],
                                           comparison_mat = survey_mat_youngest_added_fb)
}


sum_sym_avg_fb_nomask_bootstrapped <- readRDS(file.path(out.dir, 'sum_sym_avg_fb_nomask_bootstrapped.rds'))
sum_sym_avg_BICS_nomask_bootstrapped <- readRDS(file.path(out.dir, 'sum_sym_avg_BICS_nomask_bootstrapped.rds'))

ratio_bootstrapped_fb_baseline_nomask <- readRDS(file.path(out.dir, 'ratio_bootstrapped_fb_baseline_nomask.rds'))

R0_bootstrapped_polymod_baseline_nomask <- readRDS(file.path(out.dir, 'R0_bootstrapped_polymod_baseline_nomask.rds'))
R0_bootstrapped_fb_baseline_nomask <- readRDS(file.path(out.dir, 'R0_bootstrapped_fb_baseline_nomask.rds'))

# polymod baseline: R0 est + ci
R0_est_polymod_baseline_nomask <- lapply(ratio_BICS_polymod_nomask, function(x) x*baseline_R0)
ci_R0_est_polymod_baseline_nomask <- list()
for (n in 1:3) {
  ci_R0_est_polymod_baseline_nomask[[n]] <- calc_R0_ci_percentile(R0_bootstrapped_est = R0_bootstrapped_polymod_baseline_nomask[,n])
  
}

#fb baseline: R0 est + ci
R0_est_fb_baseline_nomask <- lapply(ratio_BICS_fb_nomask, function(x) x*baseline_R0)
ci_R0_est_fb_baseline_nomask <- list()
for (n in 1:3) {
  ci_R0_est_fb_baseline_nomask[[n]] <- calc_R0_ci_percentile(R0_bootstrapped_est = R0_bootstrapped_fb_baseline_nomask[,n])
  
}

```


Recreat R0 plot, showing both all contacts and contacts where no mask usage was recorded


```{r}
plot_df_r0_ci <- as.data.frame(cbind(type = "Baseline", comparison = "Baseline", contacts = "All contacts", group = "all",
                                     r0 = baseline_R0, 
                                     ci_low = baseline_R0 - 1.96*baseline_R0_SE, 
                                     ci_high = baseline_R0 + 1.96*baseline_R0_SE)) %>%
  rbind(cbind(type = "Wave 0 *", comparison = "FB", contacts = "All contacts", group = "FB, all",
              r0 = R0_est_fb_baseline[[1]], 
              ci_low = ci_R0_est_fb_baseline[[1]][1], 
              ci_high = ci_R0_est_fb_baseline[[1]][2])) %>%
  rbind(cbind(type = "Wave 1", comparison = "FB", contacts = "All contacts", group = "FB, all",
              r0 = R0_est_fb_baseline[[2]], 
              ci_low = ci_R0_est_fb_baseline[[2]][1], 
              ci_high = ci_R0_est_fb_baseline[[2]][2])) %>%
  rbind(cbind(type = "Wave 2", comparison = "FB", contacts = "All contacts", group = "FB, all",
              r0 = R0_est_fb_baseline[[3]], 
              ci_low = ci_R0_est_fb_baseline[[3]][1], 
              ci_high = ci_R0_est_fb_baseline[[3]][2])) %>%
  rbind(cbind(type = "Wave 3", comparison = "FB", contacts = "All contacts", group = "FB, all",
              r0 = R0_est_fb_baseline[[4]], 
              ci_low = ci_R0_est_fb_baseline[[4]][1], 
              ci_high = ci_R0_est_fb_baseline[[4]][2])) %>%
  rbind(cbind(type = "Wave 0 *", comparison = "POLYMOD", contacts = "All contacts", group = "POLYMOD, all",
              r0 = R0_est_polymod_baseline[[1]], 
              ci_low = ci_R0_est_polymod_baseline[[1]][1], 
              ci_high = ci_R0_est_polymod_baseline[[1]][2])) %>%
  rbind(cbind(type = "Wave 1", comparison = "POLYMOD", contacts = "All contacts", group = "POLYMOD, all",
              r0 = R0_est_polymod_baseline[[2]], 
              ci_low = ci_R0_est_polymod_baseline[[2]][1], 
              ci_high = ci_R0_est_polymod_baseline[[2]][2])) %>%
  rbind(cbind(type = "Wave 2", comparison = "POLYMOD", contacts = "All contacts", group = "POLYMOD, all",
              r0 = R0_est_polymod_baseline[[3]], 
              ci_low = ci_R0_est_polymod_baseline[[3]][1], 
              ci_high = ci_R0_est_polymod_baseline[[3]][2])) %>%
    rbind(cbind(type = "Wave 3", comparison = "POLYMOD", contacts = "All contacts", group = "POLYMOD, all",
              r0 = R0_est_polymod_baseline[[4]], 
              ci_low = ci_R0_est_polymod_baseline[[4]][1], 
              ci_high = ci_R0_est_polymod_baseline[[4]][2])) %>%
  rbind(cbind(type = "Wave 1", comparison = "FB", contacts = "Only non-masked contacts", group = "FB, no mask",
              r0 = R0_est_fb_baseline_nomask[[1]], 
              ci_low = ci_R0_est_fb_baseline_nomask[[1]][1], 
              ci_high = ci_R0_est_fb_baseline_nomask[[1]][2])) %>%
  rbind(cbind(type = "Wave 2", comparison = "FB", contacts = "Only non-masked contacts", group = "FB, no mask",
              r0 = R0_est_fb_baseline_nomask[[2]], 
              ci_low = ci_R0_est_fb_baseline_nomask[[2]][1], 
              ci_high = ci_R0_est_fb_baseline_nomask[[2]][2])) %>%
  rbind(cbind(type = "Wave 3", comparison = "FB", contacts = "Only non-masked contacts", group = "FB, no mask",
              r0 = R0_est_fb_baseline_nomask[[3]], 
              ci_low = ci_R0_est_fb_baseline_nomask[[3]][1], 
              ci_high = ci_R0_est_fb_baseline_nomask[[3]][2])) %>%
  rbind(cbind(type = "Wave 1", comparison = "POLYMOD", contacts = "Only non-masked contacts", group = "POLYMOD, no mask",
              r0 = R0_est_polymod_baseline_nomask[[1]], 
              ci_low = ci_R0_est_polymod_baseline_nomask[[1]][1], 
              ci_high = ci_R0_est_polymod_baseline_nomask[[1]][2])) %>%

  rbind(cbind(type = "Wave 2", comparison = "POLYMOD", contacts = "Only non-masked contacts", group = "POLYMOD, no mask",
              r0 = R0_est_polymod_baseline_nomask[[2]], 
              ci_low = ci_R0_est_polymod_baseline_nomask[[2]][1], 
              ci_high = ci_R0_est_polymod_baseline_nomask[[2]][2])) %>%
  rbind(cbind(type = "Wave 3", comparison = "POLYMOD", contacts = "Only non-masked contacts", group = "POLYMOD, no mask",
              r0 = R0_est_polymod_baseline_nomask[[3]], 
              ci_low = ci_R0_est_polymod_baseline_nomask[[3]][1], 
              ci_high = ci_R0_est_polymod_baseline_nomask[[3]][2])) %>%
  mutate(r0 = as.numeric(as.character(r0)), ci_low = as.numeric(as.character(ci_low)), ci_high=as.numeric(as.character(ci_high)))

R0plot <- plot_df_r0_ci %>% 
  ggplot(aes(x=type, y = r0, group = group, color = comparison, shape = contacts)) +
  scale_color_manual(name = "Relative to", values = c("black", "blue",  "maroon")) +
  geom_errorbar(width=.1, aes(ymin=ci_low, ymax=ci_high), position=position_dodge(width=0.5)) +
  geom_point(size=3, fill="white", position=position_dodge(width=0.5)) +
  scale_shape_manual(name = "", values = c(19,18)) +
  geom_hline(yintercept = 1, col = "black", linetype = "dotted")+
  labs(y = expression(R[0]~estimate), x = "")+
  theme_classic(base_size = 8) +
  theme(legend.position="bottom")

R0plot_final <- ggpubr::annotate_figure(R0plot,
                                          bottom = ggpubr::text_grob("* NB: Face mask usage data was not collected in Wave 0", color = "black",
                                                                     hjust = 1, x = 1, size = 8))


ggsave(R0plot_final, file = here("bics-paper-code", "out","R0_figure_w_no_mask.png"), width = 6, height = 4)
ggsave(R0plot_final, file = here("bics-paper-code", "out","R0_figure_w_no_mask.pdf"), width = 6, height = 4)

R0plot_final


```